Tulai

### 2023-09-01 tulai-fin.qmd
Added tulai-fin.qmd and removed Tula'i-fin.qmd

---
title: "Tulai"
author: "Setareh Shafizadeh, Ben Marwick"
date: now
format: 
  html:
    self-contained: true
execute: 
  warning: false
  fig-dpi: 600
title-block-published: "last updated"
editor: visual
---
## Introduction

@@

Should fix the error 
```{r}

@@

------------

>>>>

---
title: "Tulai"
author: "Setareh Shafizadeh, Ben Marwick"
date: now
format: 
  html:
    self-contained: true
execute: 
  warning: false
  fig-dpi: 600
title-block-published: "last updated"
editor: visual
---

## Introduction

@@

Should fix the error

@@

------------------------------------------------------------------------
